Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-25 paper/paper.tex
pass on text

\subsection{Positive Traffic}

@@

@@

\Mar{Lucas/Guilherme (CRI): precisamos dar pontape inicial propondo
  perguntas de pesquisa. Eu faco ajustes em seguida.}

>>>>

@@

\subsection{Limitations}

@@

%% \renewcommand{\labelitemi}{}
%% \setitemize[0]{leftmargin=20pt,itemindent=-20pt}
%% \begin{itemize}
%% \end{itemize}

%% \renewcommand{\labelitemi}{}
%% \setitemize[0]{leftmargin=0pt,itemindent=0pt}
%% \begin{itemize}
%%   \item{\textbf{RQ1.}~How precise is \tname?}
%%   \item{\textbf{RQ2.}~How efficient is \tname?}
%% \end{itemize}

This section reports precision and efficiency of \tname.

\subsection{Objects of Analysis}

We evaluated \tname{} on a set of attacks covering each of the four
protocols supported by Suricata and attacks with different
characteristics. Table~\ref{table:attacks} shows the attacks we
analyzed and the rule of Suricata that captures the attack. Column
``Name'' shows the name of the attack, column ``\#'' indicates whether
single or multiple messages are required to manifest the attack,
column ``Protocol'' shows the protocol name, column ``Description''
summarizes the effect of the attack, if successfull, and column
``Golden Rule'' shows the relevant parts in the options section of the
Suricata rule that captures the attack.

\begin{table*}[t!]
  \caption{\label{table:attacks}Characterization of attacks analyzed
    and Golden Rule of Suricata (reference) to capture it.}  
  \centering
  \begin{tabular}{lllll}
    \toprule
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Protocol} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{Golden Rule} \\
    \midrule
    GET/POST Flood & multiple & HTTP & Denial of Service & - \\      
    Ping Scan & single & ICMP & Discovers active hosts in a network &  - \\
    Black Nurse & multiple & ICMP & Denial of Service & - \\
    Ping Flood  & multiple & ICMP & Denial of Service & - \\  
    Port Scan TCP & single & TCP & Discovers open ports in a host & -  \\
    SYN Flood & multiple & TCP & Denial of Service & - \\
    Port Scan UDP & single & UDP & Discovers open ports in a host & - \\        
    \bottomrule
  \end{tabular}
\end{table*}

\subsection{Setup}

\Fix{any other detail we should consider?}

\subsection{Precision}

\subsection{Efficiency}
